Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-15 main_paper.tex
Conclusion

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

@@

The strategy exploits arbitrary rules used to assign treatment to units, usually
relying on some type of ``score,'' the so called running variable. In its basic 
version, units with score above a certain treshold receive treatment while the 
ones below that cutoff are left untreated.

The identification of the treatment effect at the treshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
treshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
and extensions by \cite{calonico2014} (CCT, henceforth).

@@

As pointed out by \cite{ccf2016}, ``(...)valid inference
requires the delicate balancing act of selecting a bandwidth small enough
to remove smoothing bias, yet large enough to ensure adequate precision.''
The authors compare the strategies of undersmoothing, and explicit bias 
correction concluding that direct bias-correction with the corresponding 
rescalling of the CI's is a superior approach.

@@

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD.'' We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
CCT,\footnote{Throughout the paper we follow the notation on \cite{calonico2014} very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT 
identification and inference procedures can be developed based on the following 
assumptions\footnote{The assumptions below are the same as presented by CCT.}
\begin{assumption}\label{A1}
 For some $\kappa_{0} > 0$, the following holds in the neighborhood 
 $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
 \begin{enumerate}
  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, 
  $f(x)$, is continuous and bounded away from zero.
  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=
  \mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously 
  differentiable.
  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and 
  $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous 
  and bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

CCT point out that the conventional approaches to construct 
confidence intervals for $\tau$ using the local linear estimator rely on a 
large-sample approximation for the standardized $t$-statistic that is valid only
if the bandwidth shrink fast enough to eliminate the leading bias term 
contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and 
$nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}],
  \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=
 lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=
 lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known 
 quantities that depend on the kernel and order of polynomial used in the 
 estimation. Under these conditions we could use a conventional confidence 
 interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the 
standard normal distribution. However, most approaches to select the bandwidth, 
$h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth 
selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' 
since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a 
first-order bias in the distributional approximation used to construct the 
confidence intervals.

CCT resolve the problem by deriving the analytical form of the 
first-order bias and correcting it directly. To obtain correct coverage the 
confidence interval needs not only to be recentered to correct the bias, but 
also rescaled to allow for the additional variability introduced by the bias 
correction. Their approach rely on obtaining a bias-corrected  estimator, 
$\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that 
the first-order bias term itself will depend on the bandwidth $h_{n}$. The 
approximate bias term can be described as:
\begin{align*}
     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed 
quantities that depend on the data, kernel and $h_{n}$. The plug-in 
bias-corrected estimator then requires estimates for the second derivatives of 
the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
$\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic
estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}
     \mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and 
$\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator,
\cite{calonico2014} obtain a robust confidence interval with a different 
asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if 
$n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and 
$n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< 
\kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) 
variability of the bias estimate used for correction as well as its correlation 
with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the 
formulas are currently ommitted from this paper since their form is not relevant
to the bootstrap procedure innovation proposed. The details can be found at 
CCT Appendix}  Under these conditions we can construct a valid 
confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}
  (h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}
  (h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly coverage of the CIs 
constructed and provides practitioners with a new toolset to perform inference 
that is more robust to the choice of bandwidth. We build upon the insight 
provided by CCT bias-corrected estimator and propose a simple 
bootstrap procedure that can directly construct the robust CIs without requiring
the derivation of analytical formulas and direct estimators for the bias, 
variance and covariance terms, while relying on the same first-order bias 
correction approximation proposed by that paper.

\section{Bootstrap Bias Correction}\label{boot}
Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
Intuitively, for the local-linear RD estimator's case, we will rely on a local higher-order (quadratic) polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate. This insight comes directly from CCT using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap 
bias correction procedures proposed in Section \ref{boot} produces valid, robust
confidence intervals similar to the ones obtained by the analytical procedures 
established in CCT. The bootstrap CIs obtained compare favourably
to the analytical alternative, with coverage closer to the nominal size of the 
desired test and shorter lenght of the intervals in the specifications implemented.

@@

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed 
by by\cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is
a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and 
therefore bias in the usual RD approach. For the simulation studies, we used 
250 bootstraps for bias correction, 999 bootstraps to calculate confidence 
interval and a total 500 replications. All results presented are based on a 
0.95 desired confidence level. Table \ref{Tb1} presents the main results in which
a local-linear RD estimator ($p=1$) is employed with the bias-correction based 
on a local-quadratic approximation ($q=2$). Table \ref{Tb2} presents similar 
results for $p=2$ and $q=3$.

\begin{table}[ht] \label{Tb1}
	\caption{Summary of Results ($p = 1, q = 2$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]\label{Tb2}
	\caption{Summary of Results ($p = 2, q = 3$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
		\hline
	\end{tabular}
\end{table}

As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

\section{Conclusion}\label{conclusion}

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{bootrd}

\end{document}

>>>>

\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels}
\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

@@

The strategy exploits arbitrary rules used to assign treatment to units, usually
relying on some type of ``score,'' the so called running variable. In its basic 
version, units with score above a certain threshold receive treatment while the 
ones below that cutoff are left untreated.

The identification of the treatment effect at the threshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
treshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
and extensions by \cite{calonico2014} (CCT, henceforth).

@@

As pointed out by \cite{ccf2016}, ``(...)valid inference
requires the delicate balancing act of selecting a bandwidth small enough
to remove smoothing bias, yet large enough to ensure adequate precision.''
The authors compare the strategies of undersmoothing, and explicit bias 
correction concluding that direct bias-correction with the corresponding 
rescaling of the CI's is a superior approach.

@@

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
\cite{calonico2014},\footnote{Throughout the paper we follow the
notation on CCT very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}
\begin{assumption}\label{A1}
 For some $\kappa_{0} > 0$, the following holds in the neighborhood $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
 \begin{enumerate}
  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, $f(x)$, is continuous and bounded away from zero.
  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=\mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously differentiable.
  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous and bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach rely on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth. We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation proposed by that paper.

\section{Bootstrap Bias Correction}\label{boot}

Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
Intuitively, for the local-linear RD estimator's case, we will rely on a local higher-order (quadratic) polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate. This insight comes directly from CCT using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.

@@

\section{Simulation Evidence}\label{sim}

This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in CCT. The bootstrap CIs obtained compare favorably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter length of the intervals in the specifications implemented.

@@

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications. All results presented are based on a 0.95 desired confidence level. Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table 2 presents similar results for $p=2$ and $q=3$.

\begin{table}[ht] \label{Tb1}
	\caption{Summary of estimates ($p = 1, q = 2$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]\label{Tb2}
	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
		\hline
	\end{tabular}
\end{table}
As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

\section{Conclusion}\label{conclusion}
This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in regression discontinuity designs. 
The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
Our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have improved coverage and shorter length relative to the analytical alternatives proposed by CCT.

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{bootrd}
\end{document}
